---
title: "Russian Tweets"
output:
  github_document: default
  html_notebook: default
---

# Russian Tweets (file 1 of 13)

```{r setup}
library(tidyverse)
library(lubridate)
```


## Data import

Data downloaded from [https://github.com/fivethirtyeight/russian-troll-tweets/]

```{r}
# Only the 1st file has been imported

russian_tweets_raw <- read_csv("data/Mod1/IRAhandle_tweets_1.csv")
russian_tweets_raw                                                  # print data, to look at
glimpse(russian_tweets_raw)                                         # summary, cols transposed
```


Comments on some columns (* means might be useful for viz) :

  external_author_id
  author = The handle sending the tweet
  content = The text of the tweet
  region = "United States" 159k of 244k rows, Unknown 58k, etc
  language = "English" for 190k of 244k rows; Russian 38k; Italian 6k, etc
  *publish_date = d/m/yyyy (stored as character vector) : 1st/10/11/12/13th of Jan, 2015-2018
  harvested_date = ditto-ish
  *following = The number of accounts the handle was following at the time of the tweet
  *followers = The number of followers the handle had at the time of the tweet
  updates
  post_type = Indicates if the tweet was a retweet or a quote-tweet
  account_type = Specific account theme, as coded by Linvill and Warren
  *retweet = 0 or 1
  *account_category = General account theme, as coded by Linvill and Warren
  new_june_2018 = A binary indicator of whether the handle was newly listed in June 2018


## Basic EDA

```{r}
# to get a sense of what's going on in this dataset :

russian_tweets_raw %>% count(region)             # 17 rows
russian_tweets_raw %>% count(language)           # 49 rows
russian_tweets_raw %>% count(following)          # 5780 rows ...only see the first 1000
russian_tweets_raw %>% count(account_category)   # 8 rows
russian_tweets_raw %>% count(account_type)       # 14 rows
russian_tweets_raw %>% count(post_type)          # 3 rows
russian_tweets_raw %>% count(retweet)            # 2 rows
```



```{r}
# Create dates instead of text strings (and ignore hour & minutes); use only a few of the variables :

russian_tweets <- russian_tweets_raw %>%
  mutate(tweet_date = date(mdy_hm(publish_date))) %>%
  select(account_category, region, language, following, followers, publish_date, tweet_date)

russian_tweets
```



```{r}
# 1a (scatterplot)
ggplot(russian_tweets, aes(following, followers)) +
  geom_point()

# 1b (scatterplot with facets)
ggplot(russian_tweets, aes(following, followers)) +
  geom_point() +
  facet_wrap(~ account_category)

# 2a (histogram)
ggplot(russian_tweets, aes(tweet_date)) +
  geom_freqpoly() +
  facet_wrap(~ account_category)

# 2b (filtered histogram with facets)
russian_tweets %>%
  filter(account_category == "RightTroll") %>%
ggplot(aes(tweet_date, colour = region)) +
  geom_freqpoly()

# 2c (2b with binwidth = 7, instead of default bins = 30)
russian_tweets %>%
  filter(account_category == "RightTroll") %>%
ggplot(aes(tweet_date, colour = region)) +
  geom_freqpoly(binwidth = 7)
```



